Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-20 ms.tex
more illum variation tests on 487-490

\begin{figure*}
\gridline{\fig{azlab06_illum_baseline_plot_region_488.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}
\fig{azlab06_illum_baseline_plot_region_490.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}}
\gridline{\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_488.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (488)}
\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_490.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (490)}}
\caption{There are subtle illumination pattern changes visible when average large chunks of data during the baseline test.
There is a vertical band of illumination that changes from the early versus late parts of the time series.}\label{fig:baselineIllumChange}
\end{figure*}

>>>>

\begin{figure*}
\gridline{\fig{azlab06_illum_baseline_plot_region_487.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}
\fig{azlab06_illum_baseline_plot_region_488.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}}
\gridline{\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_487.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (488)}
\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_488.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (490)}}
\caption{There are subtle illumination pattern changes visible when average large chunks of data during the baseline test.
There is a vertical band of illumination that changes from the early versus late parts of the time series.}\label{fig:baselineIllumChange487-488}
\end{figure*}

\begin{figure*}
\gridline{\fig{azlab06_illum_baseline_plot_region_489.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}
\fig{azlab06_illum_baseline_plot_region_490.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}}
\gridline{\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_489.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (488)}
\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_490.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (490)}}
\caption{There are subtle illumination pattern changes visible when average large chunks of data during the baseline test.
There is a vertical band of illumination that changes from the early versus late parts of the time series.}\label{fig:baselineIllumChange489-490}
\end{figure*}
